### 2017-02-15 2017mergingmerges/section/XX-Processes.tex
unsimplified fusion result

\begin{figure}
\begin{code}
            process
            { ins:    { s1, s2 }
            , outs:   { s3, s4 }
            , heap:   { f = T, l = 0, x1 = 0, x2 = 0}
            , label:  F0
            , instrs: { F0 = pull s1 x1              F3 {}
                      , F3 = case (f || (l /= x1))   F4 {} F5 {}
                      , F4 = push s3 x1              F5 { l = x1, f = F }
                      , F5 = pull s2 x2              F6 {}

                      , F6 = case (x1 < x2)          A0 {} B0 {}

                      , A0 = push s4 x1              A1 {}
                      , A1 = drop s1                 A2 {}
                      , A2 = pull s1 x1              A3 {}
                      , A3 = case (f || (l /= x1))   A4 {} F6 {}
                      , A4 = push s3 x1              F6 { l = x1, f = F }

                      , B0 = push s4 x2              B1 {}
                      , B1 = drop s2                 B2 {}
                      , B2 = pull s2 x2              F6 {} } }
\end{code}
\caption{Fusion of group and merge}
\label{fig:Process:Fused}
\end{figure}

>>>>

\begin{figure}
\begin{code}
            process
            { ins:    { s1, s2 }
            , outs:   { s3, s4 }
            , heap:   { f = T, l = 0, v = 0, x1 = 0, x2 = 0, b1 = 0}
            , label:  F0
            , instrs:

  (shared pull)
              { F0  = pull s1 b1            F1  {}

  (merge label B0)
              , F1  = jump                  F2  {v  = b1}

  (group labels A0-A3)
              , F2  = jump                  F3  {x1 = b1}
              , F3  = case (f || (l /= v))  F4  {}                F5  {}
              , F4  = push s3 v             F5  {l  = v, f  = F}
              , F5  = jump                  F6  {}

  (merge label B1)
              , F6  = pull s2 x2            F7  {}

  (merge label C0)
              , F7  = case (x1 < x2)        F8  {}                F16 {}

  (merge labels D0-D1)
              , F8  = push s4 x1            F9  {}
              , F9  = drop s1               F10 {}

  (shared pull)
              , F10 = pull s1 b1            F11 {}

  (group labels A0-A3)
              , F11 = jump                  F12 {v  = b1}
              , F12 = case (f || (l /= v))  F13 {}                F14 {}
              , F13 = push s3 v             F14 {l  = v, f  = F}
              , F14 = jump                  F15 {}

  (merge label D2)
              , F15 = jump                  F7  {x1 = b1}

  (merge labels E0-E2)
              , F16 = push s4 x2            F17 {}
              , F17 = drop s2               F18 {}
              , F18 = pull s2 x2            F7  {} } }
\end{code}

% With original label names and 'n', 'h' and 'p' for input state
%\begin{code}
%A0nB0n = pull s1 b1  A0pB0p{}
%A0pB0p = jump        A1hB0p{v  = b1}
%A1hB0p = jump        A1hB1h{x1 = b1}
%
%A1hB1h = case (f || (l /= v))
%                     A2hB1h{}
%                     A3hB1h{}
%
%A2hB1h = push s3 v   A3hB1h{l  = v, f  = F}
%A3hB1h = jump        A0nB1h{}
%A0nB1h = pull s2 x2  A0nC0h{}
%
%A0nC0h = case (x1 < x2)
%                     A0nD0h{}
%                     A0nE0h{}
%
%A0nD0h = push s4 x1  A0nD1h{}
%A0nD1h = drop s1     A0nD2n{}
%A0nD2n = pull s1 b1  A0pD2p{}
%A0pD2p = jump        A1hD2p{v  = b1}
%
%A1hD2p = case (f || (l /= v))
%                     A2hD2p{}
%                     A3hD2p{}
%
%A2hD2p = push s3 v   A3hD2p{l  = v, f  = F}
%A3hD2p = jump        A0nD2p{}
%A0nD2p = jump        A0nC0h{x1 = b1}
%
%A0nE0h = push s4 x2  A0nE1h{}
%A0nE1h = drop s2     A0nE2h{}
%A0nE2h = pull s2 x2  A0nC0h{}
%\end{code}

% Cleaned up, simplified, variables collated
% \begin{code}
%             process
%             { ins:    { s1, s2 }
%             , outs:   { s3, s4 }
%             , heap:   { f = T, l = 0, x1 = 0, x2 = 0}
%             , label:  F0
%             , instrs: { F0 = pull s1 x1              F3 {}
%                       , F3 = case (f || (l /= x1))   F4 {} F5 {}
%                       , F4 = push s3 x1              F5 { l = x1, f = F }
%                       , F5 = pull s2 x2              F6 {}
% 
%                       , F6 = case (x1 < x2)          A0 {} B0 {}
% 
%                       , A0 = push s4 x1              A1 {}
%                       , A1 = drop s1                 A2 {}
%                       , A2 = pull s1 x1              A3 {}
%                       , A3 = case (f || (l /= x1))   A4 {} F6 {}
%                       , A4 = push s3 x1              F6 { l = x1, f = F }
% 
%                       , B0 = push s4 x2              B1 {}
%                       , B1 = drop s2                 B2 {}
%                       , B2 = pull s2 x2              F6 {} } }
% \end{code}
\caption{Fusion of group and merge}
\label{fig:Process:Fused}
\end{figure}
